\message{ !name(target.tex)}\documentclass[12pt]{article}

\usepackage{amsmath,amsthm,amssymb}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{braket}

\newtheorem{Theorem}{Theorem}
\newtheorem{Example}{Example}

\title{Doc Title}


\begin{document}

\message{ !name(target.tex) !offset(-3) }

\maketitle
\tableofcontents

\section{Section 1 Title}


\subsection{Paragraphs}


This is a paragraph.  You just type like normal.  They are separated
by a blank line.  For example:

This is now a new paragraph.  I can italicize text with \emph{underscores}
and bold it with \textbf{asterisks}.  I can make it \texttt{monospace} using
backticks.

I will end this paragraph with another blank line and then start
talking about lists.

% This is a comment line.  It will not be rendered.

\subsection{Lists}


\begin{itemize}
\item This is an unordered list
- It will look like bullet points in the final render
- Third main item
\end{itemize}

\begin{enumerate}
\item This is a numbered list
. This is the second guy
. And so on...
\end{enumerate}

\begin{description}
\item{First Item} This is a list where the items have labels
: Second Item:: Another item
: And So On:: ...
\end{description}

\subsection{Math}


Inline math is done just using normal latex by doing  $f(x) = \exp
(-x^2)$.  Display mode is done by using a \emph{math block}, like so:


\label{eqn:f-defn}\begin{displaymath}
f(x) = \int_x^\infty g(t) dt
\end{displaymath}

Note that that  $d$ will not be upright as it should be.  We'll fix
that later.  Also note that we added an \emph{ID} to the equation.  IDs can
be added to many things.  They always appear immediately following the
thing they identify.

\subsection{Blocks}


We can do other types of blocks.  They all look the same, basically.


\begin{quote}
The internet is the most important invention since gravity.
\end{quote}

Somehow later I'll add attribution to the author.  That one is from
Einstein though.


This will show a little warning symbol next to it.


This is basically a sub-document that is allowed to have extra prereqs

\subsection{Links}


Links look like \href{https://learn.independentlearning.science/https://www.google.com}{this}.  Note that this is
an "outlink" -- a link to an external site -- and so wouldn't actually
be allowed in the main body of the document like this.  We can also
link to \href{Blocks}{headings} in the current document, or

\message{ !name(target.tex) !offset(4) }

\end{document}